README: `data-raw/analysis_datasets`

### 2024-08-10 data-raw/analysis_datasets/README.qmd

library(ManyEcoEvo)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(tibble)

# Constructed Variables Included in the ManyAnalysts meta-analysis
ManyEcoEvo_constructed_vars <-
  tribble(~response_variable_name,
          "euc_sdlgs_all",
          "euc_sdlgs>50cm",
          "euc_sdlgs0_2m",
          "small*0.25+medium*1.25+large*2.5",
          "euc_sdlgs50cm_2m",
          "average.proportion.of.plots.containing.at.least.one.euc.seedling.of.any.size",
          "day_14_weight/(day_14_tarsus_length^2)",
          "day_14_weight/day_14_tarsus_length",
          "day_14_weight*day_14_tarsus_length"
  )

@@

all_constructed_vars %>% 
  semi_join(ManyEcoEvo_constructed_vars, by) %>% 
  mutate(included_in_yi = TRUE) %>% 
  bind_rows(
    {
      all_constructed_vars %>% 
        anti_join(ManyEcoEvo_constructed_vars, by) %>% 
        mutate(included_in_yi = FALSE)
    }
  ) %>% 
  knitr::kable(col.names = c("Constructed Variable", 
                             "Included in $y_i$ meta-analysis?"), 
               format = "markdown")
```

>>>>

library(ManyEcoEvo)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(tibble)
data("ManyEcoEvo")

# Constructed Variables Included in the ManyAnalysts meta-analysis
ManyEcoEvo_constructed_vars <-
  tribble(
    ~response_variable_name,
    "euc_sdlgs_all",
    "euc_sdlgs>50cm",
    "euc_sdlgs0_2m",
    "small*0.25+medium*1.25+large*2.5",
    "euc_sdlgs50cm_2m",
    "average.proportion.of.plots.containing.at.least.one.euc.seedling.of.any.size",
    "day_14_weight/(day_14_tarsus_length^2)",
    "day_14_weight/day_14_tarsus_length",
    "day_14_weight*day_14_tarsus_length"
  )

@@

all_constructed_vars %>%
  semi_join(ManyEcoEvo_constructed_vars, by) %>%
  mutate(included_in_yi = TRUE) %>%
  bind_rows({
    all_constructed_vars %>%
      anti_join(ManyEcoEvo_constructed_vars, by) %>%
      mutate(included_in_yi = FALSE)
  }) %>%
  knitr::kable(
    col.names = c(
      "Constructed Variable",
      "Included in $y_i$ meta-analysis?"
    ),
    format = "markdown"
  )
```
